Type cones of $\b{g}$-vector fans

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex
2CY triangulated

\subsection{Statement of the theorem}
We need to introduce some notations before stating the main result of this section.  Let~$\Lambda\eqdef \End{\cat}(T)$, and let~$F$ be the functor
\[
F = \cat(T,-): \cat \xrightarrow{} \MOD \Lambda.
\]

@@

>>>>

\subsection{Statement of the theorem}\label{subsect::Statement cluster cats}
We need to introduce some notations before stating the main result of this section.  Let~$\Lambda\eqdef \End{\cat}(T)$, and let~$F$ be the functor
\[
F = \cat(T,-): \cat \xrightarrow{} \MOD \Lambda.
\]

@@

Let~$\cat$ be a triangulated category with shift functor~$\susp$.
We assume moreover that~$\cat$ is~$\field$-linear, Krull--Schmidt, Hom-finite, 2-Calabi--Yau, with a cluster-tilting object~$T$.
Then~$\cat$ satisfies all the assumptions of Setting~\ref{setting::extricat} for Section~\ref{sect::Statment extricats} but assumption (1).

We fix this issue by considering a relative extriangulated structure.
Let~$\mathbb{E}_T$ be the additive sub-bifunctor of~$\cat(-,\susp -)$ formed by those morphisms that factor through~$\add\susp T$.
Then~$(\cat,\mathbb{E}_T)$ becomes extriangulated by~\cite[Proposition 3.14]{HerschendLiuNakaoka} (this can also be checked directly).
The extriangles of~$\cat$ are precisely the triangles~$X\overset{f}{\rightarrow}Y\overset{g}{\rightarrow} Z \overset{h}{\dashrightarrow}$, for which the morphism~$h$ factors through~$\add\susp T$.
By construction, Condition (1) is now satisfied.
Moreover, the triangles appearing in Conditions (2) and (3) are extriangles for this relative structure, which shows that those two conditions are still satisfied for the extriangulated structure~$(\cat,\mathbb{E}_T)$.

\begin{remark}
The index of an object~$X$ in the triangulated category~$\cat$, coincide with its class in the Grothendieck group of~$\cat$ for the relative extriangulated structure given by~$\mathbb{E}_T$.
\end{remark}

\begin{remark}
 The main results of Section~\ref{subsect::Statement cluster cats} can thus be viewed as specific cases of the results of Section~\ref{sect::extricats}: Theorem~\ref{theo::relations-g-vecteurs} and Corollary~\ref{corollary::meshes positively generate cluster cats} are consequences of Theorem~\ref{theorem::extricats} and Corollary~\ref{corollary::meshes positively generate extricats}.
\end{remark}
